Understanding the drivers of diurnal and nocturnal urban land surface temperature

### 2018-07-15 report/article.tex
working on readme and intro for report

\begin{abstract}
Understanding the drivers of urban land thermal radiance, a key factor of land surface temperature, can assist in ameliorating the severity of the urban heat island and risk from heat waves. Of all the natural events, heat waves are among the deadliest and are likely to become longer and more frequent with climatic changes. Coupled with demographic shifts towards urban living, climate change puts significant impetus on reducing community exposure to heat waves. An understudied aspect of urban land surface temperature is factors related to nocturnal surface temperature. Nocturnal land surface temperature is important in heat wave mitigation given the urban heat island effect is most apparent during the night and the minimum nocturnal temperature is linked with heat stress and mortality. In this study, we examine the day and night urban land surface temperature (with Landsat) in seven cities across the United States. We test a series of hypotheses regarding the effect of greenspace, water bodies, and impervious surfaces on land surface temperature using advanced statistical methods. The robustness of these results is tested using different cities and satellite imagery and the results of diurnal and nocturnal analysis are compared to determine if the expected relationships hold throughout the day and night. Understanding whether the factors related to high urban temperatures are consistent across US cities is important for climate adaptation planning and capable predictive models suggest the potential for analysing the effect of potential biophysical changes might have on land surface temperature.
\end{abstract}

@@

\section{Introduction}
In a warming world, understanding the drivers of surface temperatures during both the day and night will aid in adapting cities to mitigate urban heat for the health and well being of communities.

>>>>

\begin{abstract}
Although heat waves and the urban heat island are nocturnal phenomenon, the drivers of land surface temperature during the night are poorly understood.
Given that heat waves are the deadliest natural hazard and are expected to increase in frequency and severity, determining mitigation strategies is important.
However, only recently has nocturnal imagery of cities become available by LandSat allowing nighttime land surface temperature to be analyzed.
Furthermore, it remains unclear from existing studies the independent effects of potential drivers, and their relative importance.
Here, we seek to answer the question: what are the effects and importance of drivers of land surface temperature during both day and night?
To do this, we analyze the urban land surface temperature in four cities across the United States.
We include factors related to vegetation, water, the built-environment, and topography and control them using nonlinear statistical methods which allow for their independent effects to be determined.
The results of diurnal and nocturnal analysis are compared to determine if previously reported relationships hold between cities and during both the day and night.
Understanding whether the factors related to high urban land surface temperatures are consistent across US cities is important for climate adaptation planning and during heat wave mitigation strategies.
\end{abstract}

@@

\section{Introduction}
In a warming world, understanding the drivers of surface temperatures during both the day and night will aid in adapting cities to mitigate urban heat for the health and well being of communities.
Of all the natural events, heat waves are among the deadliest and are likely to become longer and more frequent with climatic changes.
Coupled with demographic shifts towards urban living, climate change puts significant impetus on reducing community exposure to heat waves.
An understudied aspect of urban land surface temperature are factors related to nocturnal surface temperature.
Nocturnal land surface temperature is important in heat wave mitigation given the urban heat island effect is most apparent during the night and the minimum nocturnal temperature is linked with heat stress and mortality.
